Traffic Aware Resource Allocation Schemes for Multi-Cell \acs{MIMO}-\acs{OFDM} Systems

### 2014-10-09 Report/decomposition_solutions.tex
modified with markku input

To begin with, let \me{\bar{\mc{B}}_b} denote the set \me{\mc{B} \backslash \{b\}} and \me{\bar{\mc{U}}_b} represents the set \me{\mc{U} \backslash \mc{U}_b}. In order to study the decomposition based solutions, we consider the solution proposed in the \eqref{eqn-9}, which is based on the Taylor approximation for the nonconvex constraint. The following discussions are equally valid for the \ac{MSE} based solution outlined in \eqref{eqn-mse-2} as well. Since the objective of \eqref{eqn-9} can be decoupled across each \ac{BS}, the centralized problem can be equivalently written as
{\allowdisplaybreaks
\begin{IEEEeqnarray}{CCl} \label{eqn-decent-1}
\underset{\substack{\gamma_{l,k,n},\mvec{M}{k,n},\mvec{W}{k,n}, \beta_{l,k,n}}}{\text{minimize}} &\quad & \sum_{b \in \mc{B}} \| \tilde{\mbf{v}}_b \|_q \IEEEyessubnumber \label{eqn-decent-1a} \\
\text{subject to}&\quad& \eqref{eqn-9.1c} - \eqref{eqn-9.1e}, \IEEEyessubnumber
\end{IEEEeqnarray}}
where \me{\tilde{\mbf{v}}_b} denote the vector of of weighted queue deviation corresponding to the users \me{k \in \mc{U}_b}.

Following the similar approach as in \cite{pennanen2011decentralized,tolli2011decentralized}, the coupling constraint in \eqref{eqn-9.1c} or \eqref{eqn-mse-1.3} can be expressed by grouping the interference contribution from each \acp{BS} in the coordinating set \me{\mathrm{B}} as
\iftoggle{single_column}{
\begin{IEEEeqnarray}{rCl}\label{eqn-decent-3}
\beta_{l,k,n} & \geq & \sum_{\substack{j = 1\\j \neq l}}^L |\mvec{w}{l,k,n}^\herm \mvec{H}{b_k,k,n} \mvec{m}{j,k,n} |^2 \nonumber \\
&\quad& + \sum_{i \in \mc{U}_{b_k} \backslash \{k\}} \sum_{j = 1}^L |\mvec{w}{l,k,n}^\herm \mvec{H}{b_k,k,n} \mvec{m}{j,i,n} |^2 + \sum_{b \in \bar{\mc{B}}_{b_k}} \zeta_{l,k,n,b} \; + \; N_0\|\mvec{w}{l,k,n}\|^2,
\end{IEEEeqnarray}}{
\begin{multline}\label{eqn-decent-3}
	N_0\|\mvec{w}{l,k,n}\|^2 + \sum_{\substack{j = 1,j \neq l}}^L |\mvec{w}{l,k,n}^\herm \mvec{H}{b_k,k,n} \mvec{m}{j,k,n} |^2 + \sum_{b \in \bar{\mc{B}}_{b_k}} \zeta_{l,k,n,b}  \\
	+ \sum_{i \in \mc{U}_{b_k} \backslash \{k\}} \sum_{j = 1}^L |\mvec{w}{l,k,n}^\herm \mvec{H}{b_k,k,n} \mvec{m}{j,i,n} |^2 \leq \beta_{l,k,n},
\end{multline}}
where \me{\zeta_{l,k,n,b}}, which is the total interference caused by the \ac{BS} \me{b} to the \me{\ith{l}} stream of user \me{k \in \mc{U}_{b_k}} on the \me{\ith{n}} sub-channel, is upper bounded by
\begin{equation}
\zeta_{l,k,n,b} \geq \sum_{i \in \mc{U}_b} \sum_{j = 1}^L |\mvec{w}{l,k,n}^\herm \mvec{H}{b_i,k,n} \mvec{m}{j,i,n} |^2, \forall b \in \bar{\mc{B}}_{b_k}.
\end{equation}

The coupling variable \me{\beta_{l,k,n}} can be decoupled using the variable \me{\zeta_{l,k,n,b}}, which limits the interference caused by the transmission from \ac{BS} \me{b} to the user \me{\ith{k}} corresponding data stream. In order the solve for the global optimal precoders, we need to find the coupling variables \me{\zeta_{l,k,n,b}} by either \acl{PD} or by \acl{DD} method. In both approaches, the coupling constraint \eqref{eqn-9.1c} for the \ac{SCA} and \eqref{eqn-mse-1.3} for the \ac{MSE} relaxation schemes are decoupled to perform the distributed precoder design problem.

>>>>

To begin with, let \me{\bar{\mc{B}}_b} denote the set \me{\mc{B} \backslash \{b\}} and \me{\bar{\mc{U}}_b} represents the set \me{\mc{U} \backslash \mc{U}_b}. In order to study the decomposition based solutions, we consider the solution proposed in \eqref{eqn-9}, which is based on the Taylor series approximation for the nonconvex constraint. The following discussions are equally valid for the \ac{MSE} based solution outlined in \eqref{eqn-mse-2} as well. Since the objective of \eqref{eqn-9} can be decoupled across each \ac{BS}, the centralized problem can be equivalently written as
{\allowdisplaybreaks
\begin{IEEEeqnarray}{CCl} \label{eqn-decent-1}
\underset{\substack{\gamma_{l,k,n},\mvec{M}{k,n},\mvec{W}{k,n}, \beta_{l,k,n}}}{\text{minimize}} &\quad & \sum_{b \in \mc{B}} \| \tilde{\mbf{v}}_b \|_q \IEEEyessubnumber \label{eqn-decent-1a} \\
\text{subject to}&\quad& \eqref{eqn-9.1c} - \eqref{eqn-9.1e}, \IEEEyessubnumber
\end{IEEEeqnarray}}
where \me{\tilde{\mbf{v}}_b} denotes the vector of of weighted queue deviation corresponding to users \me{k \in \mc{U}_b}.

Following the similar approach as that in \cite{pennanen2011decentralized,tolli2011decentralized}, the coupling constraint in \eqref{eqn-9.1c} or \eqref{eqn-mse-1.3} can be expressed by grouping the interference contribution from each \ac{BS} in the coordinating set \me{\mathcal{B}} as
\iftoggle{single_column}{
\begin{IEEEeqnarray}{rCl}\label{eqn-decent-3}
\beta_{l,k,n} & \geq & \sum_{\substack{j = 1\\j \neq l}}^L |\mvec{w}{l,k,n}^\herm \mvec{H}{b_k,k,n} \mvec{m}{j,k,n} |^2 \nonumber \\
&\quad& + \sum_{i \in \mc{U}_{b_k} \backslash \{k\}} \sum_{j = 1}^L |\mvec{w}{l,k,n}^\herm \mvec{H}{b_k,k,n} \mvec{m}{j,i,n} |^2 + \sum_{b \in \bar{\mc{B}}_{b_k}} \zeta_{l,k,n,b} \; + \; N_0\|\mvec{w}{l,k,n}\|^2,
\end{IEEEeqnarray}}{
\begin{multline}\label{eqn-decent-3}
	N_0\|\mvec{w}{l,k,n}\|^2 + \sum_{\substack{j = 1,j \neq l}}^L |\mvec{w}{l,k,n}^\herm \mvec{H}{b_k,k,n} \mvec{m}{j,k,n} |^2 + \sum_{b \in \bar{\mc{B}}_{b_k}} \zeta_{l,k,n,b}  \\
	+ \sum_{i \in \mc{U}_{b_k} \backslash \{k\}} \sum_{j = 1}^L |\mvec{w}{l,k,n}^\herm \mvec{H}{b_k,k,n} \mvec{m}{j,i,n} |^2 \leq \beta_{l,k,n},
\end{multline}}
where \me{\zeta_{l,k,n,b}} is the total interference caused by \ac{BS} \me{b} to the \me{\ith{l}} stream of user \me{k \in \mc{U}_{b_k}} on the \me{\ith{n}} sub-channel, is upper bounded by
\begin{equation}
\zeta_{l,k,n,b} \geq \sum_{i \in \mc{U}_b} \sum_{j = 1}^L |\mvec{w}{l,k,n}^\herm \mvec{H}{b_i,k,n} \mvec{m}{j,i,n} |^2, \forall b \in \bar{\mc{B}}_{b_k}.
\end{equation}

The coupling variable \me{\beta_{l,k,n}} can be decoupled using the variable \me{\zeta_{l,k,n,b}}, which limits the total interference caused by the transmission from \ac{BS} \me{b} to the \me{\ith{l}} spatial stream of user \me{k} over the sub-channel \me{n}. In order the solve for the global optimal precoders, we need to find the coupling variables \me{\zeta_{l,k,n,b}} by either the primal or \acl{DD} method. In both approaches, the coupling constraint \eqref{eqn-9.1c} for the \ac{SCA} and \eqref{eqn-mse-1.3} for the \ac{MSE} relaxation schemes are decoupled to perform the distributed precoder design problem.

### 2014-10-09 Report/dual_approach.tex
cooker-night
modified with markku input

In this section, we discuss the \ac{ADMM} decomposition method, which is basically based on the \acl{DD}, but shows better convergence properties. In contrast to the \acl{PD} problem, the \ac{ADMM} method relaxes the interference constraints by including it in the objective function of each subproblem with a penalty pricing \cite{palomar2006tutorial,boyd2011distributed}. In order to decouple the problem \eqref{eqn-decent-1}, the coupling variables \me{\zeta_{l,k,n,b}} in \eqref{eqn-decent-3} are replaced by the respective local copies \me{\mbfa{\zeta}^{\set{b}}, \forall b \in \mc{B}}, which are then solved for an optimal solution. Now the sub problems are coupled by the global consensus vector \me{\mbfa{\zeta}} maintaining the complete stacked  interference profile of all users in the system as
\begin{IEEEeqnarray}{ll}
\mbfa{\zeta} &= \left [ \zeta_{1,\bar{\mc{U}}_{1}(1),1,1}, \dotsc, \zeta_{L,\bar{\mc{U}}_{1}(1),1,1}, \dotsc, \zeta_{L,\bar{\mc{U}}_{1}(|\bar{\mc{U}}_{1}|),1,1}, \right. \nonumber \\
& \left . \dotsc, \zeta_{L,\bar{\mc{U}}_{N_B}(|\bar{\mc{U}}_{N_B}|),1,N_B}, \dotsc, \zeta_{L,\bar{\mc{U}}_{N_B}(|\bar{\mc{U}}_{N_B}|),N,N_B} \right ] \eqspace \IEEEyessubnumber \\
n_{b_k} &= |\mbfa{\zeta}^{\set{b_k}}| = N L \sum_{b \in \mc{B}} \left | \bar{\mc{U}}_b\right |. \IEEEyessubnumber
\end{IEEEeqnarray}

Let \me{\mbfa{\zeta}(b_k)} denotes the consensus entries corresponding to the \ac{BS} \me{b_k}. Let \me{\mbfa{\nu}^{\set{b_k}}} represents the stacked dual variables corresponding to the equality condition \me{\mbfa{\zeta}^{\set{b_k}} = \mbfa{\zeta}(b_k)} used in the subproblems. In order to limit the local interference assumptions \me{\zeta^{\set{b_k}}_{l,k,n,b}} at the \acp{BS} \me{b_k}, the \ac{ADMM} method augments a scaled quadratic penalty of the interference deviation between the local and consensus value for the interference from the \ac{BS} \me{b} as \me{\zeta_{l,k,n,b}} in the objective function. At optimality, the locally assumed and the consensus interference values will be equal,  providing no contribution to the objective function. The optimal step size used to update the dual variables is the scaling factor \me{\rho} used to scale the penalty term in the objective function \cite{boyd2011distributed,bertsekas1999nonlinear}. The equality constraint for the local and the consensus interference vector \me{\mbfa{\zeta}^{\set{b_k}} = \mbfa{\zeta}(b_k)} present in each subproblem is relaxed by the taking the partial Lagrangian. Now, the subproblem at \ac{BS} \me{b} for the \me{\ith{i}} iteration is given by
\iftoggle{single_column}{

@@

Now, the local problem \eqref{eqn-dual-3} at each \ac{BS} \me{b} is solved either by the \ac{SCA} approach discussed in Section \ref{sec-3.2.1} or by using the \ac{MSE} reformulation approach outlined in Section \ref{sec-3.3}. Once the local problems are solved at each \ac{BS}, the new update for the global interference vector \me{\mbfa{\zeta}^{(i)}} and the dual variables \me{\mbfa{\nu}^{\set{b}(i)}} are performed at each \ac{BS} independently by exchanging the corresponding local copies of the interference vector \me{\mbfa{\zeta}^{\set{b}(i)}, \forall b \in \mc{B}}. Since the entries in \me{\mbfa{\zeta}^{(i)}} relates exactly two \acp{BS} only, each entry in the \me{\mbfa{\zeta}^{(i)}} can be updated by exchanging the local copies from the corresponding two \acp{BS} only. For instance, the entry \me{\zeta^{(i)}_{l,\mc{U}_{b_k}(1),n,b}} depends on the local interference value \me{\zeta^{\set{b_k}(i)}_{l,\mc{U}_{b_k}(1),n,b}} assumed by the \ac{BS} \me{b_k} and the actual interference caused by the \ac{BS} \me{b} as in \me{\zeta^{\set{b}(i)}_{l,\mc{U}_{b_k}(1),n,b}} as
\begin{equation}
\zeta_{l,\mc{U}_{b_k}(1),n,b}^{(i)} = \frac{1}{2} \, \left ( \, \zeta^{\set{b}(i)}_{l,\mc{U}_{b_k}(1),n,b} + \zeta^{\set{b_k}(i)}_{l,\mc{U}_{b_k}(1),n,b} \, \right ).
\label{zeta_update}
\end{equation}
The dual variable vector \me{\mbfa{\nu}^{\set{b_k}}}, which is the stacked dual variables of the interference equality constraint at the \ac{BS} \me{b_k}, are updated using the subgradient as
\begin{equation}\label{dual-sg-update}
\nu^{\set{b_k}(i)}_{l,k,n,b} = \nu^{\set{b_k}(i-1)}_{l,k,n,b} + \rho \, \left (\zeta^{\set{b_k}(i)}_{l,k,n,b} - \zeta^{(i)}_{l,k,n,b} \right ).
\end{equation}
The distributed precoder design using \ac{ADMM} approach is shown in Algorithm \ref{algo-3}.
{\allowdisplaybreaks 
\begin{algorithm}
	\SetAlgoLined
	\DontPrintSemicolon
	\BlankLine
	\SetKwInput{KwInit}{Initialize}
	\KwIn{\me{a_k, \, Q_k, \, \mvec{H}{b,k,n},\; \fall b \in \mathcal{B}, \, \fall k \in \mathcal{U}, \fall n \in \mathcal{N}}}
	\KwOut{\me{\mvec{m}{l,k,n}} and \me{\mvec{w}{l,k,n} \fall l \in \set{1,2,\dotsc,L}}}
	\KwInit{\me{i=0} and the transmit precoders \me{\tilde{\mbf{m}}_{l,k,n}} randomly satisfying total power constraint \eqref{eqn-4.3}}
	update \me{\mvec{w}{l,k,n}} with \eqref{eqn-10} and \me{\tilde{\mbf{u}}_{l,k,n}} with \eqref{eqn-8} \;
	initialize the global interference vectors \me{\mbfa{\zeta}^{(0)} = \mbfa{0}^{\mathrm{T}}} \;
	initialize the interference threshold \me{\mbfa{\nu}^{\set{b}(0)} \forall b \in \mc{B} = 0} \;
	\ForEach{\ac{BS} \me{b \in \mc{B}}}{
		\Repeat{convergence or \me{i \geq I_{\max}}}{
			initialize \me{j=0} \;
			\Repeat{convergence or \me{j \geq J_{\max}}}{
				solve for \me{\mvec{M}{k,n}} and the local interference \me{\mbfa{\zeta}^{\set{b}}} using \eqref{eqn-dual-3} \;
				exchange \me{\mbfa{\zeta}^{\set{b}(j)}} among \acp{BS} in \me{\mc{B}} \;
				update dual variables in \me{\mbfa{\nu}^{\set{b}(j+1)}} using \eqref{dual-sg-update}\;
				update the consensus vector \me{\mbfa{\zeta}^{(j+1)}} using \eqref{zeta_update}\;
				\me{j = j + 1}\;
			}
			downlink precoded pilot transmission with \me{\mvec{M}{k,n}}\;
			update \me{\mvec{W}{k,n}} and notify to all \acp{BS} in \me{\mc{B}} using uplink precoded pilots as in \cite{komulainen2013effective}\;
			update \me{\tilde{\mbfa{u}}_{l,k,n}} using \eqref{eqn-6.3} and \eqref{eqn-wsrm-expr} for \ac{SCA} or \me{\tilde{\epsilon}_{l,k,n}} using \eqref{eqn-mse-1.3} for \ac{MSE} approach \;
			$i = i + 1$ \;
		}
	}
	\caption{Distributed \ac{JSFRA} scheme using \ac{ADMM}}
	\label{algo-3}
\end{algorithm}}

>>>>

The \ac{ADMM} decomposition method is based on the \acl{DD}, however it shows better convergence properties. In contrast to the \acl{PD} problem, the \ac{ADMM} method relaxes the interference constraints by including it in the objective function of each subproblem with a penalty pricing \cite{palomar2006tutorial,boyd2011distributed}. In order to decouple the problem \eqref{eqn-decent-1}, the coupling variables \me{\zeta_{l,k,n,b}} in \eqref{eqn-decent-3} are replaced by the respective local copies \me{\mbfa{\zeta}^{\set{b}}, \forall b \in \mc{B}}, which are then solved for an optimal solution. Now the sub problems are coupled by the global consensus vector \me{\mbfa{\zeta}} maintaining the complete stacked  interference profile of all users in the system as
\begin{IEEEeqnarray}{ll}
\mbfa{\zeta} &= \left [ \zeta_{1,\bar{\mc{U}}_{1}(1),1,1}, \dotsc, \zeta_{L,\bar{\mc{U}}_{1}(1),1,1}, \dotsc, \zeta_{L,\bar{\mc{U}}_{1}(|\bar{\mc{U}}_{1}|),1,1}, \right. \nonumber \\
& \left . \dotsc, \zeta_{L,\bar{\mc{U}}_{N_B}(|\bar{\mc{U}}_{N_B}|),1,N_B}, \dotsc, \zeta_{L,\bar{\mc{U}}_{N_B}(|\bar{\mc{U}}_{N_B}|),N,N_B} \right ] \eqspace \IEEEyessubnumber \\
n_{b_k} &= |\mbfa{\zeta}^{\set{b_k}}| = N L \sum_{b \in \mc{B}} \left | \bar{\mc{U}}_b\right |. \IEEEyessubnumber
\end{IEEEeqnarray}

Let \me{\mbfa{\zeta}(b_k)} denote the consensus entries corresponding to \ac{BS} \me{b_k}. Let \me{\mbfa{\nu}^{\set{b_k}}} represent the stacked dual variables corresponding to the equality condition \me{\mbfa{\zeta}^{\set{b_k}} = \mbfa{\zeta}(b_k)} used in the subproblems. In order to limit the local interference assumptions \me{\zeta^{\set{b_k}}_{l,k,n,b}} in \ac{BS} \me{b_k}, the \ac{ADMM} method augments a scaled quadratic penalty of the interference deviation between the local and consensus value for the interference from the \ac{BS} \me{b} as \me{\zeta_{l,k,n,b}} in the objective function. At optimality, the locally assumed and the consensus interference values will be equal,  providing no contribution to the objective function. The optimal step size used to update the dual variables is the scaling factor \me{\rho} used to scale the penalty term in the objective function \cite{boyd2011distributed,bertsekas1999nonlinear}. The equality constraint for the local and the consensus interference vector \me{\mbfa{\zeta}^{\set{b_k}} = \mbfa{\zeta}(b_k)} present in each subproblem is relaxed by the taking the partial Lagrangian. Now, the subproblem at \ac{BS} \me{b} for the \me{\ith{i}} iteration is given by
\iftoggle{single_column}{\allowdisplaybreaks

@@

Now, the local problem \eqref{eqn-dual-3} at each \ac{BS} \me{b} is solved either by the \ac{SCA} approach discussed in Section \ref{sec-3.2.1} or by using the \ac{MSE} reformulation approach outlined in Section \ref{sec-3.3}. Once the local problems are solved at each \ac{BS}, the new update for the global interference vector \me{\mbfa{\zeta}^{(i)}} and the dual variables \me{\mbfa{\nu}^{\set{b}(i)}} are performed at each \ac{BS} independently by exchanging the corresponding local copies of the interference vector \me{\mbfa{\zeta}^{\set{b}(i)}, \forall b \in \mc{B}}. Since the entries in \me{\mbfa{\zeta}^{(i)}} relate exactly to two \acp{BS} only, each entry in \me{\mbfa{\zeta}^{(i)}} can be updated by exchanging the local copies from the corresponding two \acp{BS}. For instance, the entry \me{\zeta^{(i)}_{l,\mc{U}_{b_k}(1),n,b}} depends on the local interference value \me{\zeta^{\set{b_k}(i)}_{l,\mc{U}_{b_k}(1),n,b}} assumed by the \ac{BS} \me{b_k} and the actual interference caused by \ac{BS} \me{b} as in \me{\zeta^{\set{b}(i)}_{l,\mc{U}_{b_k}(1),n,b}} as
\begin{equation}
\zeta_{l,\mc{U}_{b_k}(1),n,b}^{(i)} = \frac{1}{2} \, \left ( \, \zeta^{\set{b}(i)}_{l,\mc{U}_{b_k}(1),n,b} + \zeta^{\set{b_k}(i)}_{l,\mc{U}_{b_k}(1),n,b} \, \right ).
\label{zeta_update}
\end{equation}
The dual variable vector \me{\mbfa{\nu}^{\set{b_k}}}, which includes the stacked dual variables of the interference equality constraint at \ac{BS} \me{b_k}, are updated using the subgradient as
\begin{equation}\label{dual-sg-update}
\nu^{\set{b_k}(i)}_{l,k,n,b} = \nu^{\set{b_k}(i-1)}_{l,k,n,b} + \rho \, \left (\zeta^{\set{b_k}(i)}_{l,k,n,b} - \zeta^{(i)}_{l,k,n,b} \right ).
\end{equation}
The distributed precoder design using \ac{ADMM} approach is shown in Algorithm \ref{algo-3}.
{\allowdisplaybreaks 
\begin{algorithm}
	\SetAlgoLined
	\DontPrintSemicolon
	\BlankLine
	\SetKwInput{KwInit}{Initialize}
	\KwIn{\me{a_k, \, Q_k, \, \mvec{H}{b,k,n},\; \fall b \in \mathcal{B}, \, \fall k \in \mathcal{U}, \fall n \in \mathcal{N}}}
	\KwOut{\me{\mvec{m}{l,k,n}} and \me{\mvec{w}{l,k,n} \fall l \in \set{1,2,\dotsc,L}}}
	\KwInit{\me{i=0} and the transmit precoders \me{\tilde{\mbf{m}}_{l,k,n}} randomly satisfying total power constraint \eqref{eqn-4.3}}
	update \me{\mvec{w}{l,k,n}} with \eqref{eqn-10} and \me{\tilde{\mbf{u}}_{l,k,n}} with \eqref{eqn-8} \;
	initialize the global interference vectors \me{\mbfa{\zeta}^{(0)} = \mbfa{0}^{\mathrm{T}}} \;
	initialize the interference threshold \me{\mbfa{\nu}^{\set{b}(0)} \forall b \in \mc{B} = 0} \;
	\ForEach{\ac{BS} \me{b \in \mc{B}}}{
		\Repeat{convergence or \me{i \geq I_{\max}}}{
			initialize \me{j=0} \;
			\Repeat{convergence or \me{j \geq J_{\max}}}{
				solve for \me{\mvec{M}{k,n}} and the local interference \me{\mbfa{\zeta}^{\set{b}}} using \eqref{eqn-dual-3} \;
				exchange \me{\mbfa{\zeta}^{\set{b}(j)}} among \acp{BS} in \me{\mc{B}} \;
				update dual variables in \me{\mbfa{\nu}^{\set{b}(j+1)}} using \eqref{dual-sg-update}\;
				update the consensus vector \me{\mbfa{\zeta}^{(j+1)}} using \eqref{zeta_update}\;
				\me{j = j + 1}\;
			}
			downlink precoded pilot transmission with \me{\mvec{M}{k,n}}\;
			update \me{\mvec{W}{k,n}} and notify to all \acp{BS} in \me{\mc{B}} using uplink precoded pilots as in \cite{komulainen2013effective}\;
			update \me{\tilde{\mbfa{u}}_{l,k,n}} using \eqref{eqn-6.3} and \eqref{eqn-wsrm-expr} for \ac{SCA} or \me{\tilde{\epsilon}_{l,k,n}} using \eqref{eqn-mse-1.3} for \ac{MSE} approach \;
			$i = i + 1$ \;
		}
	}
	\caption{Distributed \ac{JSFRA} scheme using \ac{ADMM}}
	\label{algo-3}
\end{algorithm}}

### 2014-10-09 Report/ieee_journal.tex
modified with markku input

\documentclass[10pt,final,twocolumn,letterpaper]{./../Styles/IEEEtran}

@@

\title{Traffic Aware Resource Allocation Schemes for Multi-Cell \acs{MIMO}-\acs{OFDM} Systems}
\author{
	\IEEEauthorblockN{Ganesh Venkatraman, Antti T\"{o}lli, Le-Nam Tran and Markku Juntti}
	\IEEEauthorblockA{Centre for Wireless Communications (CWC), Department of Communications Engineering (DCE), \\
		University of Oulu, Oulu, FI-90014\\
		Email: \{gvenkatr, antti.tolli, le.nam.tran, markku.juntti\}@ee.oulu.fi}
}

@@

\subsection{\acs{JSFRA} scheme via \ac{SCA} approach} \label{sec-3.2.1}
\input{problem_formulation}
\input{wsrm_formulation}

\subsection{\ac{JSFRA} scheme via \ac{MSE} reformulation} \label{sec-3.3}
\input{mse_formulation}

\subsection{Reduced Complexity Resource Allocation (Per Sub-Channel Resource Allocation)} \label{sec-3.4}
\input{sub_channel_wsrm}

@@

\subsection{Decomposition using \ac{KKT} equations in \ac{MSE} formulation} \label{sec-4.3}

@@

\section*{Acknowledgment}
This work has been supported by the Finnish Funding Agency for Technology and Innovation (Tekes), Nokia Solutions Networks, Xilinx Ireland, Academy of Finland.

>>>>

\documentclass[10pt,final,twocolumn,a4paper]{./../Styles/IEEEtran}

@@

\title{Traffic Aware Resource Allocation Schemes for Multi-Cell \acs{MIMO}-\acs{OFDM} Systems}
\author{
	\IEEEauthorblockN{Ganesh Venkatraman \IEEEmembership{Student Member,~IEEE}\thanks{This work has been supported by the Finnish Funding Agency for Technology and Innovation (Tekes), Nokia Solutions Networks, Xilinx Ireland, Academy of Finland.}, Antti T\"{o}lli \IEEEmembership{Member,~IEEE}, Le-Nam Tran \IEEEmembership{Member,~IEEE}, and Markku Juntti \IEEEmembership{Senior Member,~IEEE}}\thanks{
	The authors are with the Centre for Wireless Communications (CWC), Department of Communications Engineering (DCE), University of Oulu, Oulu, FI-90014, (e-mail: \{gvenkatr, antti.tolli, le.nam.tran, markku.juntti\}@ee.oulu.fi).}}

@@

\subsection{\acs{JSFRA} Scheme via \ac{SCA} approach} \label{sec-3.2.1}
\input{problem_formulation}
\input{wsrm_formulation}

\subsection{\ac{JSFRA} Scheme via \ac{MSE} Reformulation} \label{sec-3.3}
\input{mse_formulation}

\subsection{Reduced Complexity Resource Allocation} \label{sec-3.4}
\input{sub_channel_wsrm}

@@

\subsection{Decomposition Using \ac{KKT} Equations in \ac{MSE} Formulation} \label{sec-4.3}

@@

### 2014-10-09 Report/introduction.tex
modified with markku input

In general, the resource allocation problems are formulated by assigning a binary variable to each user indicating the presence or the absence of a particular resource \cite{admission_control}. In contrast to that, we use linear transmit precoders, which are the complex vectors, as a decision variable in determining the presence or the absence of a user on a particular resource. The purpose is two-fold. Firstly, the formulation determines the transmission rate on a certain resource, and, secondly, by making the transmit beamformer of a particular user to be a zero vector, the corresponding user will not be scheduled on a certain resource.

>>>>

In general, the resource allocation problems are formulated by assigning a binary variable to each user indicating the presence or the absence in a particular resource \cite{admission_control}. In contrast to that, we use linear transmit precoders, which are the complex vectors, as a decision variable in determining the presence or the absence of a user on a particular resource. The purpose is two-fold. Firstly, the formulation determines the transmission rate on a certain resource, and, secondly, by making the transmit beamformer of a particular user to be a zero vector, the corresponding user will not be scheduled on a certain resource.
